Standartox

### 2020-04-09 README.Rmd
release 0.1

Standartox is a data base tool standartizing the retrieval and aggregation of ecotoxicological test data. It is based on the [EPA ECOTOX data base](https://cfpub.epa.gov/ecotox/) as well as on data from several other chemical data bases and allows users to filter and aggregate ecotoxicological test data in an easy way. It can either be accessed via a [web-app](http://standartox.uni-landau.de/) or via the R-package [standartox](https://github.com/andschar/standartox). Ecotoxicological test data are used in environmental risk assessment to calculate effect measures such as [TU - Toxic Units](https://en.wikipedia.org/wiki/Toxic_unit) or [SSD - Species Sensitivity Distributions](https://edild.github.io/ssd/) to asses toxicity of chemicals.

The project lives in these three repositories:

- [standartox-build](https://github.com/andschar/standartox-build) - Compiles the tool
- [standartox-app](https://github.com/andschar/standartox-app) - Serves the website and API
- [standartox](https://github.com/andschar/standartox) - R-package

>>>>

Standartox is a database and tool facilitating the retrieval of ecotoxicological test data. It is based on the [EPA ECOTOX data base](https://cfpub.epa.gov/ecotox/) as well as on data from several other chemical databases and allows users to filter and aggregate ecotoxicological test data in an easy way. It can either be accessed via a [web-app](http://standartox.uni-landau.de/) or via the R-package [standartox](https://github.com/andschar/standartox). Ecotoxicological test data is used in environmental risk assessment to calculate effect measures such as [TU - Toxic Units](https://en.wikipedia.org/wiki/Toxic_unit) or [SSD - Species Sensitivity Distributions](https://edild.github.io/ssd/) to asses environmental toxicity of chemicals.

The project lives in two repositories:

  - [standartox-build](https://github.com/andschar/standartox-build) - Compiles and serves database
  - [standartox](https://github.com/andschar/standartox) - R-package
